### 2022-02-26 tikz/xlrm.tex
some edits by JDG, going to send to Klaus for feedback

\usepackage{xcolor}
\definecolor{giallo}{HTML}{F0BC42}
\definecolor{rosso}{HTML}{8E1F2F}
\definecolor{grigio}{HTML}{CACACC}
\definecolor{nero}{HTML}{000000}
\definecolor{thirds}{HTML}{31467A}
\definecolor{orange}{HTML}{F18101}
\definecolor{deepblue}{HTML}{CA3CFF}

@@

    \node [font=\color{rosso}\selectfont] at (-4.5, 3.5) {\Large Uncertainties};
    \node [relation] (relationships) at (0, -0.5) {Cost and damage models};
    \node [uncertainty] (surge) at (-3.25, 2.5) {Storm surge\\{\footnotesize (draws from 1 posterior)}};
    \path [line] (surge) to (relationships);

    \node [font=\color{thirds}\selectfont] at (0, -1.75) {\Large Relationships};
    \node [uncertainty] (slr) at (-3.5, -1) {Sea level rise\\{\footnotesize (16 PDFs)}};
    \path [line] (slr) to (relationships);

>>>>

\usepackage{xcolor}
\definecolor{giallo}{HTML}{F0BC42}
\definecolor{rosso}{HTML}{8E1F2F}
\definecolor{grigio}{HTML}{CACACC}
\definecolor{nero}{HTML}{000000}
\definecolor{thirds}{HTML}{31467A}
\definecolor{orange}{HTML}{F18101}

@@

    \node [font=\color{rosso}\selectfont] at (-4.5, 3.5) {\Large Uncertainties};
    \node [relation] (relationships) at (0, -0.5) {Engineering and economic models};
    \node [uncertainty] (surge) at (-3.25, 2.5) {Storm surge\\{\footnotesize (draws from 1 posterior)}};
    \path [line] (surge) to (relationships);

    \node [font=\color{thirds}\selectfont] at (0, -1.75) {\Large Relationships};
    \node [uncertainty] (slr) at (-3.5, -1) {Sea level\\{\footnotesize (16 PDFs)}};
    \path [line] (slr) to (relationships);
